%------------------------
  % Resume in Latex
  % Author: Jake Gutierrez
  % Based off of: https://github.com/sb2nov/resume
  % License: MIT
  %------------------------

  \documentclass[letterpaper,11pt]{article}

  \usepackage{latexsym}
  \usepackage[empty]{fullpage}
  \usepackage{titlesec}
  \usepackage{marvosym}
  \usepackage[usenames,dvipsnames]{color}
  \usepackage{verbatim}
  \usepackage{enumitem}
  \usepackage[hidelinks]{hyperref}
  \usepackage{fancyhdr}a
  \usepackage[english]{babel}
  \usepackage{tabularx}
  \usepackage{fontawesome5}
  \usepackage{multicol}
  \setlength{\multicolsep}{-3.0pt}
  \setlength{\columnsep}{-1pt}
  \input{glyphtounicode}
  \usepackage{ragged2e}

  \usepackage{xcolor}
  \hypersetup{colorlinks,urlcolor=blue}


  %----------FONT OPTIONS----------
  % sans-serif
  % \usepackage[sfdefault]{FiraSans}
  % \usepackage[sfdefault]{roboto}
  % \usepackage[sfdefault]{noto-sans}
  % \usepackage[default]{sourcesanspro}

  % serif
  % \usepackage{CormorantGaramond}
  \usepackage{charter}


  \pagestyle{fancy}
  \fancyhf{} % clear all header and footer fields
  \fancyfoot{}
  \renewcommand{\headrulewidth}{0pt}
  \renewcommand{\footrulewidth}{0pt}

  % Adjust margins
  \addtolength{\oddsidemargin}{-0.7in}
  \addtolength{\evensidemargin}{-0.7in}
  \addtolength{\textwidth}{1in}
  \addtolength{\topmargin}{-.7in}
  \addtolength{\textheight}{1.0in}

  \urlstyle{same}

  \raggedbottom
  \raggedright
  \setlength{\tabcolsep}{0in}

  % Sections formatting
  \titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
  }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

  % Ensure that generate pdf is machine readable/ATS parsable
  \pdfgentounicode=1

  %-------------------------
  % Custom commands
  \newcommand{\resumeItem}[1]{
    \item\small{
      {#1 \vspace{-2pt}}
    }
  }
  \hypersetup{%
    colorlinks=true,% hyperlinks will be colored
    linkcolor=blue,% hyperlink text will be green
    linkbordercolor=blue,% hyperlink border will be red
  }

  \newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        {#1} & #2 \\
        \textit{\small#3} & \textit{\small #4}\\
      \end{tabular*}\vspace{-7pt}
  }

  \newcommand{\resumeCertheading}[2]{
    \vspace{5pt}\item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        {#1} & #2 \\
      \end{tabular*}\vspace{-7pt}
  }

  \newcommand{\resumeEduheading}[5]{
    \vspace{2pt}\item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        {#1} & #2 \\
        \textit{\small#3} & \textit{\small #4}\\
        \textit{\small#5} \\
      \end{tabular*}\vspace{-7pt}
  }

  \newcommand{\resumeSubSubheading}[2]{
      \item
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
      \end{tabular*}\vspace{-7pt}
  }

  \newcommand{\resumeProjectHeading}[2]{
      \item
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \\
      \end{tabular*}\vspace{-7pt}
  }

  \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

  \renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

  \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
  \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
  \newcommand{\resumeItemListStart}{\begin{itemize}}
  \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

  %-------------------------------------------
  %%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
  \textbf{\Huge \scshape Shanu Tiwari} \\ \vspace{1pt}
  \href{tel:7879810036}{+91 7879810036} $|$
  {Indore, India} $|$
  {Frontend Developer} $|$
  \href{mailto:shanutiwari.work@gmail.com}{shanutiwari.work@gmail.com} \\ \vspace{1pt}

  \href{https://linkedin.com/in/shanutiwari1010}{\underline{linkedin.com/in/shanutiwari1010}} $|$
  \href{https://github.com/shanutiwari1010}{\underline{github.com/shanutiwari1010}} $|$
  \href{https://twitter.com/shanutiwari1010}{\underline{twitter.com/shanutiwari1010}}$|$
   \href{https://shanutiwari.me/}{\underline{shanutiwari.me}} 
  
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeEduheading
{Medi-Caps University}{Indore, Madhya Pradesh}
{Bachelor of Technology in Computer Science and Engineering}{September 2020 -- July 2024}
{CGPA: 8.7/10}
\resumeEduheading
{Sanskar Academy, CBSE}{Pachore, Madhya Pradesh}
{12th, Mathematics}{April 2018 -- July 2020}
{Percentage: 87\%}
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{: \hfill JavaScript, Java, HTML, CSS, SQL \hfill} \\
        \vspace{3pt}\textbf{Libraries/Frameworks}{: \hfill React, Tailwind, Bootstrap, Shadcn, Apexcharts, NodeJS, Express.JS \hfill} \\
        \vspace{3pt}\textbf{Databases}{: \hfill MongoDB, MySQL, Redis \hfill} \\
        \vspace{3pt}\textbf{Platforms/Tools}{: \hfill Vercel, Git, GitHub Pages, Figma \hfill} \\
        }}
\end{itemize}

% ---------- EXPERIENCE ----------

\section{Experience}
\resumeSubHeadingListStart

% ------------------------
\resumeSubheading
{\textbf{\href{https://www.techlene.com/}{Techlene Software Solutions}\hspace{5pt}}{{[JavaScript, React, ApexCharts, Redis]}}}{(On Site) Indore, India}
{\textbf{Software Development Engineer – Intern}}{March 2024 -- Present}
\resumeItemListStart
\resumeItem{Integrated ApexCharts library for interactive graphs, enhancing dashboard usability.}
\resumeItem{ Improved app speed and reliability by using Redis to store and manage data effectively.}
\resumeItem{Engineered a user-friendly dashboard with React components, optimizing navigation and data visualization for better decision-making.}
\resumeItemListEnd
\resumeSubHeadingListEnd
% ------------------------



%-----------PROJECTS-----------
\section{Projects}

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://money-tracker-app-gamma.vercel.app/}{Pocket Money Tracker}\hspace{5pt}}{[HTML, CSS, ReactJS, MongoDB, Express.JS, NodeJS]}}{}
\resumeItemListStart
\resumeItem{Pocket Money Tracker is a web application designed for easy and comprehensive financial management.}
\resumeItem{Using HTML and CSS for a user-friendly interface that looks great on any device.}
\resumeItem{Pocket Money Tracker is a financial transaction tracking tool that uses React.js for seamless tracking and MongoDB for secure storage and quick data retrieval.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://shanutiwari1010.github.io/currency-converter/}{Currency Converter}\hspace{5pt}}{{[HTML, CSS, JavaScript]}}}{}
\resumeItemListStart
\resumeItem{Crafted a robust currency converter tool leveraging HTML, CSS, and JavaScript, facilitating effortless currency conversions for users.}
\resumeItem{Designed an intuitive user interface for enhanced usability and streamlined conversion experience.}
\resumeItem{Integrated real-time currency exchange rate updates to provide accurate financial information for users.}
\resumeItemListEnd
\resumeSubHeadingListEnd

% \resumeSubHeadingListStart
% \resumeProjectHeading
% {\textbf{\href{https://github.com/ayushsoni1010/mapsearchify}{The Style Factory}\hspace{5pt}}{{[HTML, CSS]}}}{}
% \resumeItemListStart
% \resumeItem{Created and implemented a graphical user interface (UI) using HTML and CSS for a fashionable clothing brand.}
% \resumeItem{Responsive design made it possible for customers to shop with ease and explore the newest styles on all devices.}
% \resumeItem{Showcased a trendy clothing brand through a stylish and responsive website, providing an immersive and user-friendly platform for fashion enthusiasts.}
% \resumeItemListEnd
% \resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/shanutiwari1010/react-practice-projects/tree/main/03-todo}{Task Manager}\hspace{5pt}}{{[ReactJS, Tailwind]}}}{}
\resumeItemListStart
\resumeItem{Created task manager with React and Tailwind CSS for efficient task organization.
}
\resumeItem{Developed a dynamic todo list with features such as task addition, deletion, and updates using React's component architecture.}
\resumeItem{Enhanced user interface and responsiveness using Tailwind CSS, ensuring seamless task management across devices.}


\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Trainings/Certifications}
\resumeSubHeadingListStart
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeCertheading
{\textbf{\href{https://medicaps.ac.in/}{Industrial Training}\hspace{5pt}}{{[Machine Learning]}}}{Medicaps University, Indore}
\resumeItemListStart
\resumeItem{successfully completed a 6-week online training on Data Science. The training 
consisted of Introduction to Data Science, Python for Data Science, Understanding the Statistics for Data 
Science, Predictive Modeling and Basics of Machine Learning, and The Final Project modules. }
\resumeItemListEnd

\resumeCertheading
{\textbf{\href{https://coursera.org/verify/FHDUZAK7YL3Q}{Crash Course on python}\hspace{3pt}}{{}}}{coursera}
\resumeItemListStart
\resumeItem{Completed a beginner-friendly Python Crash Course on Coursera, mastering the basics of coding and problem-solving in Python}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
